Gravitational waves from colliding black holes

### 2017-04-14 Report/Draft/draft.tex

\begin{abstract}
B B B B B Binnnaryyyy.. 
\end{abstract}

@@

We first consider in closer detail the effects of precession on a GW waveform. A closer look at equation (16), which essentially quantifies the amount of precession in a given binary, shows that it takes values in the range $[0,1]$, when the spin on the larger BH is fully in-plane. Even for a maximally precessing signal however, many possible configurations of polarisation and inclination are possible. We show this in Fig. 7, where from this particular perspective the precessive effect appears largest in the case of the in-plane spin being $0.5$, instead of the maximally precessing system with $|\vec{S}|=0.98$. In this case this is due to the fact that the inclination angle is defined with respect to the total angular momentum, and so when we say we are viewing a binary 'edge-on', i.e. at $\iota=\pi/2$, the actual orbital plane of the system will not necessarily be edge-on at all for precessing systems. As a result, it is not always the case that precession affects are most noticeable in systems with the most precession, and a lot depends on the specific combination of source location and the polarisation and inclination angles for a specific event.

>>>>

\begin{abstract}pdftotext draft.pdf - | wc -w
B B B B B Binnnaryyyy..

\end{abstract}

@@

We first consider in closer detail the effects of precession on a GW waveform. A closer look at equation (16), which essentially quantifies the amount of precession in a given binary, shows that it takes values in the range $[0,1]$, when the spin on the larger BH is fully in-plane. Even for a maximally precessing signal however, many possible configurations of polarisation and inclination are possible which will affect the way the amplitude of the signal is modulated. We show this in Fig. 7, where from this particular perspective the precessive effect appears largest in the case of the in-plane spin being $0.5$, instead of the maximally precessing system with $|\vec{S}|=0.98$. In this case this is due to the fact that the inclination angle is defined with respect to the total angular momentum, and so when we say we are viewing a binary 'edge-on', i.e. at $\iota=\pi/2$, the actual orbital plane of the system will not necessarily be edge-on at all for precessing systems. As a result, it is not always the case that precession affects are most noticeable in systems with the most precession, and a lot depends on the specific combination of source location and the polarisation and inclination angles for a specific event.
